Deadlock Freedom on Self-Assembled DNA Nano Networks

### 2013-11-04 trunk/PAPER/implementation.tex
monteleone's fixes

\begin{figure}
  \centering
  \includegraphics[width=0.25\textwidth]{pictures/disr_imp.eps}
  \caption{\emph{DiSR} block architecture.}
 \label{fig:implementation}
\end{figure}

Let's so focus to the \emph{DiSR} block. In
Fig.~\ref{fig:implementation} is shown a possible sketch of this
block, which mainly consist in the following building elements:

\begin{itemize}
\item \emph{DBS block}: It Takes trace of the DBS, and how already
discussed in the Section~\ref{ssec:disr_dstruct}, there are six possible
configurations. These values can be codified using 3 bit implemented
with a 3-bit register and the required combinational logic. This block
is essentially designed as a state machine.
\item \emph{LED registers}: Is a set of registers useful for storing
the local environment data (LED) described in
Section~\ref{ssec:disr_dstruct}. In particular in
fig.~\ref{fig:implementation}, are highlighted two tables representing
the \emph{link\_visited[]} and \emph{link\_tvisited[]} values. This
block consists of an array of registers (one for each
direction) that can be implemented with an SRAM, in which are presents
two specific fields  for representing the \emph{segID}. 
\item \emph{Control circuitry}: This circuitry reads data
from the fields of the incoming packet, LED registers and the
\emph{DBS}, updating \emph{LED} and
\emph{DBS} data when required. Then, the resulting \emph{Ctrl Out} output  drives the other
communication resources (such as node transceivers) for actuating the
DiSR routing operation.
\end{itemize}

As discussed above, one of the main design challenge of DNA
Self-Assembled systems is the limited resource available for
implementing both computations and routing decisions for each node.
For this reason, assuming a budget of $10^4$ CNFETs for each network's
node~\cite{liu_jetcs} we estimated the required resource for
implementing the entire DiSR block. A not optimized behavioural
HDL of the DiSR circuitry has been written and synthesized at gate-level.
Considering the specific layout of each single logic elements ( NAND,
full-adder, latch etc.), it has been possible to get a rough estimate
of the number of transistors necessary for implementing the DiSR
logic.  Figure~\ref{fig:imp_trend} shows the results of synthesis in
terms of number of devices (CNFETs) versus the number of network nodes
while the network scales up from $10\times10$ to $100\times100$ nodes.
\begin{figure}
  \centering
  \includegraphics[width=0.25\textwidth]{pictures/imp_rslt.eps}
  \caption{Number of network's node (N) vs number of CNFETs.}
 \label{fig:imp_trend}
\end{figure}
In particular, observing the Fig.\ref{fig:imp_trend} can 
be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
Further, more than the absolute number of devices itself, it is interesting to
observe that, while the node have a squared increment, the circuitry
complexity which implements the DiSR algorithm increases with a slowly
growing trend.  
An intuitive explanation of this is the relatively simple logic of
DiSR, whose behaviour is almost code on scalable storage structures.
For example, the number of registers implementing the
\emph{link\_visited[]} and \emph{link\_tvisited[]} table follow the
logarithmic function:
\begin{equation}
  \label{eq:imp_trend}
  N_{reg}=2\cdot N_{port} \cdot log_2(N)
\end{equation}
where $N_{port}$ is the number of the router's ports, $N$ is the number 
of network's nodes while the term $2$ takes in account that \emph{link\_visited[]} and 
\emph{link\_tvisited[]} are two separate set of registers. While this number is fixed by 
the number of network's node, the control circuitry could be optimized applying more effort 
in future designs of this building block.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{pictures/implementation.eps}
  \caption{\emph{DiSR} block architecture.}
 \label{fig:implementation}
\end{figure}

To give a basic estimate of the overhead needed we will focus on
DiSR-specific components, that is, the control logic and configuration
registers needed to implement DiSR. In
Figure~\ref{fig:implementation} is shown a sketch of a possible
implementation, which mainly consist in the following building
elements: 
\begin{itemize}
	\item \textbf{DBS block:} It takes trace of the DBS state machine, 
	consisting of a 3-bit register (to cover six DBS values) and the 
	required combinational logic. This block receives signals from 
	stored packets to decode the packet type, and from 
	the control circuitry to change its status.
	The bootstrap node is selected by setting the boot signal to high
	during the initialization phase.  
	\item \textbf{LED registers:} A set of registers storing 
	the \emph{LED} listed in the section
	\ref{sec:disr_concepts}. It should be pointed out that, while the \emph{visited} 
	and \emph{tvisited} data must be implemented with two distinct
	elements, the \emph{tvisited} and \emph{visited} table can be implemented with 
	a single RAM file for storing the segment id of each link.
	This can be done adding a special register named \emph{Tflag}
	indicating whether the \emph{SegID} value refers to \emph{visited} or to 
	\emph{tvisited}. When SegID's register is set to 0, it means that the link
	is neither visited nor tvisited.

    \item \textbf{Control circuitry:} This circuitry reads data from
	the incoming packet, the LED registers and the DBS,
	updating them when required. This block drives the LED register 
	for storing or, for reading the LED data according with
	\emph{write enable (WE)} or \emph{read enable (RE)}
	signals. Then, the resulting \emph{Ctrl-Out} drives the other
	communication resources for actuating the DiSR routing operation.
\end{itemize}

Each building block reacts with the rising edge  of
the\emph{clock signal} shown in Figure. An asynchronous system
\emph{reset} signal is also present for restoring all registers to
their default values. When this last signal is
set, the DBS state machines for each network's node are set as
\emph{Free}.

As discussed above, one of the main design challenge of DNA
Self-Assembled systems is the limited resource available for
implementing both computations and routing decisions for each node.
Assuming a budget of $10^4$ CNFETs for each network's
node~\cite{liu_jetcs}  we estimated the required resources for
implementing the entire DiSR block.  A not optimized RTL description
(with an hardware description language)  of the DiSR circuitry has
been written and synthesized at gate-level. Considering the specific
layout of each single logic elements (NAND, full-adder, latch etc.),
it has been possible to get a rough estimate of the number of
transistors necessary to implement the DiSR logic.

Figure~\ref{fig:imp_trend} shows the results of synthesis in
terms of number of devices (CNFETs) versus the number of network nodes
while the network scales up from $10\times10$ to $100\times100$ nodes.
\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{pictures/imp_rslt.eps}
  \caption{Number of network's node (N) vs number of CNFETs.}
 \label{fig:imp_trend}
\end{figure}
In particular, observing the Figure~\ref{fig:imp_trend} can 
be pointed out that the proposed implementation occupies about 17\% of the node budget. 
Further, more than the absolute number of devices itself, it is interesting to
observe that, while the node have a squared increment, the circuitry
complexity which implements the DiSR algorithm increases with a slowly
growing trend.  
An intuitive explanation of this is the relatively simple logic of
DiSR, whose behaviour is al4ost code on scalable storage structures.
For example, the number of registers
implementing the \emph{link\_visited[]} and \emph{link\_tvisited[]}
table follow the logarithmic function $N_{reg}=N_{port} \cdot
log_2(N)$ where \emph{Nport} is the number of the router’s ports, N is
the number of network’s nodes.  While $N_{reg}$ is fixed by the number
of network’s node,  the control circuitry could be optimized applying
more effort in future designs of this building block.

### 2013-11-04 trunk/PAPER/introduction.tex
monteleone's fixes

These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be founded on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altougth we can assume an architecture similar to the
one depicted in Figure~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not strictly dependent on any of the
underlying computing architecture.

%where instructions and data operands travel
%on packets and routed using a topology-agnostic strategy that avoids
%deadlock, 
\begin{figure}
  \centering
    \includegraphics[width=0.20\textwidth]{pictures/dna1.eps}
  \caption{Irregular topology of computing and storage elements}
  \label{fig:nana}
\end{figure}

In this paper we introduce DiSR, a first effort for a Distributed
Segment-based Routing in large scale DNA self assembled networks.
The main contribution is to bring the advantages of
a segment-based approach~\cite{mejia_ipdps06} to deadlock freedom without requiring any topology graph,
external defect map or centralized algorithm execution. 
While maintaining similar properties to segment-based , the DiSR
approach is not intended to discover the "optimal" segment choice
(ideally reachable with the knowledge of the topology graph) but just
to demonstrate a concrete model that can fit into such complex,
irregular and large sized topologies.
Given the irregular/high-defect rates scenario discussed above, is essential
avoiding non-scalable or resource hungry solutions such as
centralized off-chip algorithms, tree-based approaches, virtual channels
or expensive implementations based on hardware redundancy.

>>>>

\begin{figure}
\centering
\begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
 (a) & (b)
 \end{tabular}
  \caption{DNA tag matching and Resulting Irregualr Topology}
  \label{fig:nana}
\end{figure}
These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be based on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see Figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altougth we can assume an architecture similar to the
one depicted in Figure~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not strictly dependent on any of the
underlying computing architecture.

In this work we introduce DiSR, a Distributed Segment-based approach
to deadlock freedom in large scale DNA self assembled networks. Our
contribution aims to achieve the classical properties of a
segment-based approach~\cite{mejia_ipdps06} without requiring any
topology graph, external defect map or centralized algorithm
execution.  So the DiSR approach is not intended to discover the
``optimal'' segment choice (ideally reachable with the knowledge of
the topology graph) but just to demonstrate a concrete model that can
fit into such complex, irregular and large sized networks.

### 2013-11-04 trunk/PAPER/simulation.tex
Fixes pic captions
monteleone's fixes

\section{Simulation environment}

In this section we will test the proposed DiSR approach to demonstrate
its effectiveness from two different perspectives:
\begin{itemize}
\item Against the centralized segment based approach (SR), to evaluate
if and how its known properties are still preserved in the new nano-scale distributed scenario
\item Against topology agnostic approaches based on spanning
trees and broadcasting, to measure how DiSR performs in discovering
the network structure 
\end{itemize}

\subsection{Nanoxim tool}

In order to quantitatively and qualitatively evaluate the proposed approach a
specific simulation environment has been developed, resulting in
the open source and freely available project called Nanoxim~\cite{}.
Nanoxim is a SystemC tool based on a almost rewritten
version of the Noxim Network-on-Chip simulator~\cite{}. While some
complex features have been removed (e.g. wormhole, congestion/topology
aware routing and selection strategies) new features specifically
taylored for nanoscale scenario were introduced, e.g. the ability to simulate a random
network, the implementation of the DiSR to obtain the segment topology
and the support for defective links and nodes.

%------------------------------------------------------------------------------
\subsection{Experimental setup}
The following parameters have been taken into account when
performing the DiSR simulation:
\begin{itemize}
\item {S}: Size of the network, intended as number of nodes, on a
range from 10x10 to 100x100 sized networks. 
\item {\% defective links}: the probability that each link is
disconnected or not present, from 0 the amount that yelds
no more segments.
\item {\% defective nodes}: the probability that a node is not
working, thus having all its attached links not useful for DiSR setup.
Same range as defective links parameter.
\item {Bootstrap node}: the node used from upper layer (e.g. microscale)
to inject the DiSR process. When not explicitly investigating the
impact of each single bootstrap choice, a set representative regions have been
considered, i.e. the central part of the network and the edge corners
\end{itemize}

The show the results, the following evaluation metrics have been adopted:
\begin{itemize}
\item{Node coverage}: this is the fraction of nodes that
are assigned to a segment. In the ideal case, all the non defective
nodes should be assigned, so this metric is useful to show how some
disconnected node regions can negativaly impact on the whole DiSR
effectiveness.
\item{Broadcast latency}: this measures how the time required to complete the
segment assignment scale for increasing network sizes and defect rates
\item{Bootstrap node effect}: this evaluates the impact of the chosen
bootstrap node on the node coverage.
\end{itemize}

Further, to evaluate how DiSR compares against the centralized segment
based algorithm, the following metrics have been adopted:
\begin{itemize}
\item {Average Path Lenght}:
\item {Average Link Weight}:
\item {Unidirectional restrictions:}
\item {Number of Segments}:
\end{itemize}

Since the distribution of defects and thus the resulting topology is randomly
generated, a set of simulations with different seeds has been run
for each system configuration. We found that TODO repetitions are
required in order to obtain statistically significant results.

\subsection{Other optimisations}
Some optimisation parameters, which demostrated to improve the DiSR
results have been fixed to some good values, but are not subject to
further investigation; once again the focus here is not the
optimal set of segments, but just demostrating a working approach. 
These are optimisations are:
\begin{itemize}
\item{cycle\_links}: max number of retries across the set of links of
each node. While searching for a free link due an incoming request,
the same request is cancelled after a given number of tries. This
gives to preceding node change to test a different paths. Default is set to 1.
\item{bootstrap\_timeout}: number of time units that a bootstrap node
should wait before assuming that a livelock in the starting segment
process has occurred. In the worst case, we can imagine that longest
path required is the one returning to the bootstrap node after having
travelled across all the links. So, althought this is just an extreme
situation, a good upper limit can be safely be set to NxN.
\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
setup process, a bootstrap node should not have defective links.
Enabling this optimisation, a bootstrap node is immune to defects.
We may think of a pre-boostrap phase that properly selects (from upper
layer via) a bootstrap node which is tested as properly connected. We
enabled this optimisation, however empirical tests showed us that only
simulations using bootstrap nodes placed on edges would be heavily
affected, since these are nodes starting with a lower number of links,
e.g. corner nodes could only have two connected direction, so even a
defective link could prevent starting segment packet to return to
bootstrap to close the loop a create the segment.

\end{itemize}

\section{Results}
\label{sec:results}

In Figure~\ref{fig:coverage} is shown node coverage using different
network sizes and bootstrap injection points. As can be seen,
increasing the \% of defective node, TODO COMMENT...

\begin{figure*}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/set1.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/set3.eps} \\
    (a) & (b)
  \end{tabular}
  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
  \label{fig:coverage}
\end{figure*}

Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
on node coverage, for different defect rates. TODO COMMENT.

%\begin{figure}
%  \centering
%  \begin{tabular}{cc}
%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
%    (a) & (b)
%  \end{tabular}
%  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
%  \label{fig:bootstrap}
%\end{figure}

Next, Figure~\ref{fig:latency_size} shows latency as function of
network size, with different defect rates, while Figure~\ref{fig:latency_defective}
shows the same latency when different bootstrap nodes are
considered.... TODO COMMENT

TODO: something like Broadcast Tree properties (sez.  5.4)

>>>>

\section{Simulation and Results}
\label{sec:simulation}

In this section we will test the proposed DiSR approach to demonstrate
its effectiveness and compare it against topology agnostic approach
based on spanning trees and
broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how DiSR
performs in covering the network structure.

%\item Against the centralized segment based approach (SR), to evaluate
%if and how its known properties are still preserved in the new nano-scale distributed scenario

\subsection{Nanoxim Environment}

In order to quantitatively and qualitatively evaluate the proposed approach a
specific simulation environment has been developed, resulting in
the open source and freely available project called
Nanoxim~\cite{nanoxim}.
Nanoxim is a SystemC tool based on a almost rewritten
version of the Noxim Network-on-Chip simulator~\cite{noxim}. While some
complex features have been removed (e.g. wormhole, congestion/topology
aware routing and selection strategies) new features specifically
taylored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
network, the implementation of the DiSR to obtain the segment topology
and the support for defective links and nodes.

%------------------------------------------------------------------------------
\subsection{Experimental setup}
The following parameters have been taken into account when
performing the DiSR simulation:
\begin{itemize}
\item {\emph{Size of the network}}: number of nodes, on a range from
10x10 to 100x100 sized networks. 
%\item {\% defective links}: the probability that each link is
%disconnected or not present, from 0 the amount that yelds
%no more segments.
\item {\emph{\% defective nodes}}: the probability that a node is not
working, thus having all its links cannot be utilized during DiSR setup.  
%Same range as defective links parameter.
\item {\emph{Bootstrap node}}: the node used from upper layer 
to inject the DiSR process. When not explicitly investigating the
impact of each single bootstrap choice, a set representative regions have been
considered, e.g. the central part of the network and the edge corners.
\end{itemize}
To present the results, the following evaluation metrics have been adopted:
\begin{itemize}
\item{Node coverage}: this is the fraction of nodes that
are assigned to a segment. In the ideal case, all the non defective
nodes should be assigned, so this metric is useful to show how some
disconnected regions can negatively impact on the whole DiSR
effectiveness.
\item{\emph{Latency}}: this measures how the cycles required to complete the
segment assignment scales for increasing network sizes and defect rates
\item{\emph{Bootstrap node effect}}: this evaluates the impact of the chosen
bootstrap node on the node coverage.
\end{itemize}

%Further, to evaluate how DiSR compares against the centralized segment
%based algorithm, the following metrics have been adopted:
%\begin{itemize}
%%\item {Average Path Lenght}:
%%\item {Average Link Weight}:
%\item {Unidirectional restrictions:}
%\item {Number of Segments}:
%\end{itemize}

Since the distribution of defects and thus the resulting topology is randomly
generated, a set of simulations with different seeds has been run
for each system configuration. We found that 20 repetitions are
required in order to obtain statistically significant results.

% TODO: long paper
\subsection{Other Optimisations}
Some optimisation parameters, which demostrated to improve the DiSR
results have been fixed to some good values, but are not subject to
further investigation; once again the focus here is not the
optimal set of segments, but just demostrating a working approach. 
These are optimisations are:
\begin{itemize}
\item{cycle\_links}: max number of retries across the set of links of
each node. While searching for a free link due an incoming request,
the same request is cancelled after a given number of tries. This
gives to preceding node change to test a different paths. Default is set to 1.
\item{bootstrap\_timeout}: number of time units that a bootstrap node
should wait before assuming that a livelock in the starting segment
process has occurred. In the worst case, we can imagine that longest
path required is the one returning to the bootstrap node after having
travelled across all the links. So, althought this is just an extreme
situation, a good upper limit can be safely be set to NxN.
\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
setup process, a bootstrap node should not have defective links.
Enabling this optimisation, a bootstrap node is immune to defects.
We may think of a pre-bootstrap phase that properly selects (from upper
layer via) a bootstrap node which is tested as properly connected. We
enabled this optimisation, however empirical tests showed us that only
simulations using bootstrap nodes placed on edges would be heavily
affected, since these are nodes starting with a lower number of links,
e.g. corner nodes could only have two connected direction, so even a
defective link could prevent starting segment packet to return to
bootstrap to close the loop a create the segment.
\end{itemize}

\subsection{Results}
\label{sec:results}

In this section we analyze the results in terms of node
coverage and latency at different network sizes, defect rates and
bootstrap injection points.  In particular
Figure~\ref{fig:results_coverage} shows
node coverage for DiSR and RPF tree based approach respectively. While
the first aim of DiSR is not to reach the optimal coverage, we still
can observe a quite good performance as compared to the tree based
approach. Note that defect rates beyond 25\% lead to many disconnected
regions of nodes that DiSR currently cannot handle.
For example Figure~\ref{fig:net} show a 30x30 network with a 25\%
defect in which the bottom-left part cannot be reached due
disconnected regions. Note that remaining defective nodes belonging to
connected regions are successfully surrounded by DiSR coverage; in any
case, these defect levels should be considered as worst case scenarios, so the
achieved coverage of $0.5$ is a satisfying result for this first
version of DiSR. On the other hand, the network size seems to have a
limited impact when defect rate do not introduce too much disconnected
regions. 
\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.48\textwidth]{pictures/set1.eps} & 
\includegraphics[width=0.48\textwidth]{pictures/coverage.eps} \\
(a) & (b) 
\end{tabular}
\caption{DiSR (a) and RPF (b) node coverage}
\label{fig:results_coverage}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.70\textwidth]{pictures/net.ps}
\caption{Covered regions in a 30x30 network with 25\% defects}
\label{fig:net}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
\includegraphics[width=0.48\textwidth]{pictures/set2.eps} & 
\includegraphics[width=0.48\textwidth]{pictures/set2_rpf.eps} \\
(a) & (b)
\end{tabular}
\caption{Latency of DiSR (a) vs tree based RPF (b) }
\label{fig:results_latency}
\end{figure}

The number of cycles required to complete segment mapping process
is shown in Figure~\ref{fig:results_latency}. In this case comparison
against tree-based shows better (lower) values at different defect
rates.  Rather than the absolute numbers, what it's more interesting
to observe is how DiSR latency scales with network size. For example,
going from 900 to 2500 nodes, at the medium defect rate of $0.15$,
leads to an increase from 3000 to 4500 cycles. It should be noticed
also how the effect of defect rate is increasing until the threshold
of $0.25$ is reached, meaning that until that limit DiSR finds it more
and more difficult to complete the process due increasing defective
paths, but still discover new segments when let running for a more
extended amount of cycles. This behavior is not reported in the RPF
based approach, meaning that a tree based approach, although starting
from higher values, is less affected by defect rates (when low rates
are considered).
After the $0.25$ threshold, the impact of entire disconnected regions
becomes predominant and both approaches become faster in completing
the covering process, since far less nodes can be actually reached.

Finally, Figure~\ref{fig:results_bootstrap} visually represents  the
stability of the approach against choices of a different bootstrap
node in a 10x10 network.  This is an important aspect to evaluate when
considering that one of the main advantages of DiSR against all the
tree based approaches should be the ability of choosing whatever
bootstrap node, without having to care about the role assumed in the
future by the chosen root node.  In other words, after segments have
been established, the bootstrap node is like every other node, i.e. it
is not center of a structure, and it is not an hotspot for the traffic
distribution. The results in terms of coverage,  shown for low, medium
and high defect profiles, demonstrate a relatively limited
impact of the bootstrap choice in the low/medium scenarios, while a
$30\%$ instability is found for very high defect rates. This also
sounds acceptable, since when a lot of defective nodes are present, the
particular position of the bootstrap node could lead to a completely
different evolution in the DiSR setup process.

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{pictures/set3.eps}
\caption{Effect of bootstrap node}
\label{fig:results_bootstrap}
\end{figure}
